---
title: "Gather Dataframes"
author: "Sam Portnow"
date: "`r Sys.Date()`"
output:
  tufte::tufte_html: default
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
link-citations: yes
---


In my previous analysis, I put the json the  [Clinical Trials API](https://clinicaltrials.gov/api/gui) into dataframes, where each study was saved as a separate dataframe. Now, I want to read all that information in and store it into larger datasets.

```{r}
library(tidyverse)
library(here)
library(fs)
library(feather)
```

First lets look at the files

```{r look}
data_files = dir_ls(here::here('data', 'raw'), type = 'file')

data_files[sample(length(data_files), 10)]
```

Everything is split out by a - 

```{r split}

data_file_types = str_extract(data_files, '-.*') %>% str_replace('-', '') %>% str_replace('.feather', '') %>% unique()
data_file_types
data_files_types = na.omit(data_file_types)
```

Okay, so there are 10 data file types. Let's put walk over theme bind all the info we need, and write out our big dataset. 

```{r write_feather}

walk(data_file_types, function(x){
  
  print (x)
  
  data_sub = data_files[str_detect(data_files, x)]
  data_write = map_dfr(data_sub, read_feather)  
  write_feather(data_write, here::here('data', paste0(x, '.feather')))
  
})

```


```{r}

```

