---
title: "InvestigateDataSets"
author: "Sam Portnow"
date: "5/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(feather)
library(skimr)
library(gt)
library(here)
library(fs)
library(janitor)
library(refinr)
library(gtsummary)
```

# Introduction

I downloaded datasets from the clinical trials API. It's time to clean them up. 

# Baseline Datasets

## Baseline Measures

## Baseline Category

```{r}
b_cat = read_feather(here::here('data', 'BaselineCategoryList.feather'))
skim(b_cat)
```
Let's look at some individual rows.

```{r}

b_cat %>% sample_n(5) 

```


## Baseline Class Denominator

## BaslineGroup

```{r}

b_group = read_feather(here::here('data', 'BaselineGroup.feather'))
skim(b_group)
  
```
This dataset contains information about the different baseline groups. Let's take a closer look

```{r}
b_group %>% sample_n(10) 
```
This is very important information! It tells me everything I need to know about the groups. I'm going to have to do a lot of cleaning to the GroupTitle. There are many different ways that a title can be parsed, so I'm going to try to label it! To do that, I'm going to write out the data to a text file and send it up to my (doccano app)[https://psyc-articles.herokuapp.com]. Doccano is a great open source tool for annotating documents. 

```{r}

write_lines(b_group$BaselineGroupTitle, here::here('output', 'baseline_group_titles.txt'))

write_lines(b_group %>% 
              filter(! is.na(BaselineGroupDescription)) %>% 
              filter(str_squish(BaselineGroupDescription) != '') %>% 
              filter(nchar(BaselineGroupDescription) > 5) %>% 
              sample_frac(1) %>% pull(BaselineGroupDescription) %>% str_squish(), here::here('output', 'baseline_group_descriptions.txt'))

```


